### 2022-01-27 input/conclusion.tex
stupid comment
comments from the thursday meeting

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible traffic between \processes.  In this paper, we
tackled the problem of content indexing, a key service for storage
systems.
%
We proposed to address this problem as a dynamic logical partitioning
where partitions grow and shrink to reflect content and replicas
locations, as well as infrastructure changes. Using an efficient
communication primitive called scoped broadcast, each \process
composing the infrastructure eventually knows the \process hosting the
best replica of specific content.  The challenge resides in handling
concurrent operations that may impair the propagation of messages, and
in turn, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

\noindent As future work, we plan to evaluate \NAME within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of \NAME in a real system subject to high dynamicity, and
compare it against its current DHT-based indexing system that does not
include distance in its operation.

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing, a key service for storage systems, as a
dynamic logical partitioning problem where partitions grow and shrink
to reflect content and replicas locations, as well as infrastructure
changes.

Using an efficient
communication primitive called scoped broadcast, each \process
composing the infrastructure eventually knows the \process hosting the
best replica of a specific content.  The challenge resides in handling
concurrent operations that may impair the propagation of messages, and
in turn, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.  We also
briefly discussed an improvement to contain the traffic in relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

\noindent As future work, we plan to evaluate \NAME within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of \NAME in a real system subject to high dynamicity, and
compare it against its current DHT-based indexing system that does not
include distance in its operation.
\note{Parler de l'application au CDN (voir tex)}

### 2022-01-27 input/experiments.tex
comments from the thursday meeting

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution. We set the weight of links between 5 and 15 at random
following a uniform distribution also. Weights and latency are different,
hence the first $\alpha$ received by a \process may not be that of its
shortest path. It implies more concurrent operations, hence more
traffic to reach consistent partitioning.\note{Pour moi ce n'est pas assez claire pourquoi more traffic to reach CP +proposition de reformulation voir tex}
% Weight and latency are different in order to imply more concurrent operations (hence more traffic to reach consistent partitioning): the first $\alpha$ received by a node may not be that of its shortest path.

@@

\noindent Therefore, the first partition is the most expensive, for $\alpha$'s\note{'s pas compris? all $alpha$ sounds better?}
must reach every \process which takes time and generate more traffic.
\NAME quickly converges towards consistent partitioning in only\note{in only... why only? compare to what ? Is it good bad? why?}
% we should give additional elements to explain why it is rather ok to converge in 350ms: maybe by underlining the nb of nodes and the average latency between nodes.
350 milliseconds. The last and $100^{th}$ partition added around 21
seconds is the least expensive. By using scoped broadcast, control
information only reaches a small subset of the whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$'s and $\delta$'s. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 creations and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead \note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
when there is no operation in the system. \NAME's overhead actually
depends on its usage.

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures composed of multilple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks by using another
    Edge infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} \note{Ici c'est Géant aussi. pourquoi nous n'avions pas 40 ASes dans l'experience précedente + Mentionné que c'est une vision de Geant?}
     as depicted in Figure~\ref{fig:europe-ases} (a). \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

>>>>

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partionning.

@@

\noindent Therefore, the first partition is the most expensive, for
$\alpha$ messages must reach every \process which takes time and
generate more traffic.  \NAME quickly converges towards consistent
partitioning in 350 milliseconds.
% TODO: Is 350ms is the optimal? if so it would be great to explain it.
The last and $100^{th}$ partition
added around 21 seconds is the least expensive. By using scoped
broadcast, control information only reaches a small subset of the
whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$ and $\delta$ messagess. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 creations and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
%\note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
 when there is no operation in the system. \NAME's overhead actually
depends on its usage.

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multilple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks, following the
    GEANT network and the underlying European NRENs.
    Figure~\ref{fig:europe-ases} (a) depicts the resulting
    infrastructure composed of 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}. \emph{Gateway} \processes (dark
    in the figure) link autonomous systems together, \eg a Lisbon
    \node links Portugal to Spain and United Kingdoms through a Madrid
    \node and a London \node respectively.
